### 2018-10-27 Paper/app.tex
..

The computational cost is estimated in terms of the number of function evaluations or model runs,
denoted by $\mathcal{M}$ in each case. In the case of DGSM-based approach presented in this work, 
$\mathcal{M}$ = $N(N_p+1)$ ($N$: number of samples, $N_p$: number of parameters)
as discussed earlier in~\ref{sub:dgsm}. In the case of PCE-based computation of $\mathcal{T}(\theta_i)$,
$\mathcal{M}$ is the sum total of the number of training points used for constructing the sparse-basis
PCE and the number of evaluations used for its verification, denoted by $N_v$. In Table~\ref{tab:cost},
we provide a comparison of $\mathcal{M}$ for the two approaches in the case of 19 and 33 uncertain
parameters for the H$_2$/O$_2$ reaction kinetics application. 
%
\begin{table}[htbp]
\renewcommand{\arraystretch}{1.5}
\caption{A comparison of computational cost for the DGSM-based and Sobol'-based parametric 
sensitivity analysis in the case of 19 and 33 uncertain rate-controlling parameters.}
\begin{center}
\begin{tabular}{c|c|c|}
\cline{2-3}
& \multicolumn{2}{ c| }{$\mathbf{\#}$ \textbf{of Function Evaluations/Model Runs}~($\mathcal{M}$)} \\ \cline{2-3} 
& \textbf{19D} & \textbf{33D} \\  \hhline{===}
\multicolumn{1}{ |l|| }{\textbf{DGSM-based}, $\widehat{\mathcal{C}_i\mu_i}$} & 5(19+1) = 100 & 5(33+1) = 170 \\ 
\cline{1-3}
\multicolumn{1}{ |l|| }{\textbf{Total-effect Sobol'}, $\mathcal{T}(\theta_i)$} & 20 + $N_v$ & 
500 + $N_v$ \\ \cline{1-3}  
\end{tabular}
\end{center}
\label{tab:cost}
\end{table}
%
For the 19D case, estimating the converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$)
required 5 samples. However, since finite difference was used in this work for estimating the gradient of the
model output, a total of 100 model runs were required. However, as mentioned earlier in~\ref{sub:dgsm}, depending
upon the application, it is possible to explore efficient techniques for gradient estimation such as those involving 
adjoint computation and automatic differentiation. Hence, there is scope for reduction in the computational cost
associated with the DGSM-based approach. Constructing the sparse-basis PCE requires only 20 samples in
the 19D parameter space with uncertain pre-exponents. However, additional model runs typically ranging from
$\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$ are needed to build a cross validation test suite to verify the 
accuracy of the PCE. The DGSM-based approach could thus yield computational gains especially when 
efficient gradient computation techniques are used. The comparison is significantly more favorable for the 
proposed DGSM-based framework in the higher dimensional case involving 33 uncertain parameters. 
Once again, converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) are obtained
using only 5 samples in the 33D parameter space. Hence, a total of 170 model runs are needed in this case
including for gradient computation using finite difference. Whereas,
constructing the sparse PCE itself requires model runs at 500 training points to sufficiently converge. Additional
model runs are required to further verify the accuracy of the resulting PCE. Note that the analysis was performed
for the fuel-rich case. However, similar trends are expected for the fuel-lean case and we do not include them here
for brevity.

In addition to the potential for computational cost reduction using the proposed framework, the comparative 
analysis also reveals the significant increase in computational effort pertaining to the estimation of the total-effect
Sobol' indices as the dimensionality increases from 19 to 33 despite using an efficient approach involving
sparse-basis PCEs. It can thus be understood that for higher dimensional problems involving hundreds of 
parameters, conventional approaches can quickly become prohibitive and the proposed framework could help
reduce the computational effort by several orders of magnitude.

>>>>

The computational cost is estimated in terms of the number of function evaluations or model runs,
denoted by $\mathcal{M}$ in each case. In the case of DGSM-based approach presented in this work, 
$\mathcal{M}$ = $N(N_p+1)$ ($N$: number of samples, $N_p$: number of parameters)
as discussed earlier in~\ref{sub:dgsm}. In the case of PCE-based computation of $\mathcal{T}(\theta_i)$,
$\mathcal{M}$ is the sum total of the number of training points used for constructing the sparse-basis
PCE and the number of evaluations used for its verification, denoted by $N_v$. In Table~\ref{tab:cost},
we provide a comparison of $\mathcal{M}$ for the two approaches in the case of 19 and 33 uncertain
parameters for the H$_2$/O$_2$ reaction kinetics application. 
%
\begin{table}[htbp]
\renewcommand{\arraystretch}{1.5}
\caption{A comparison of computational cost for the DGSM-based and Sobol'-based parametric 
sensitivity analysis in the case of 19 and 33 uncertain rate-controlling parameters.}
\begin{center}
\begin{tabular}{c|c|c|}
\cline{2-3}
& \multicolumn{2}{ c| }{$\mathbf{\#}$ \textbf{of Function Evaluations/Model Runs}~($\mathcal{M}$)} \\ \cline{2-3} 
& \textbf{19D} & \textbf{33D} \\  \hhline{===}
\multicolumn{1}{ |l|| }{\textbf{DGSM-based}, $\widehat{\mathcal{C}_i\mu_i}$} & 5(19+1) = 100 & 5(33+1) = 170 \\ 
\cline{1-3}
\multicolumn{1}{ |l|| }{\textbf{Total-effect Sobol'}, $\mathcal{T}(\theta_i)$} & 20 + $N_v$ & 
500 + $N_v$ \\ \cline{1-3}  
\end{tabular}
\end{center}
\label{tab:cost}
\end{table}
%
For the 19D case, estimating the converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$)
required 5 samples. However, since finite difference was used in this work for estimating the gradient of the
model output, a total of 100 model runs were required. However, as mentioned earlier in~\ref{sub:dgsm}, depending
upon the application, it is possible to explore efficient techniques for gradient estimation such as those involving 
adjoint computation and automatic differentiation. Hence, there is scope for reduction in the computational cost
associated with the DGSM-based approach. Constructing the sparse-basis PCE requires only 20 samples in
the 19D parameter space with uncertain pre-exponents. However, additional model runs typically ranging from
$\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$ are needed to build a cross validation test suite to verify the 
accuracy of the PCE. The DGSM-based approach could thus yield computational gains especially when 
efficient gradient computation techniques are used. The comparison is significantly more favorable for the 
proposed DGSM-based framework in the higher dimensional case involving 33 uncertain parameters. 
Once again, converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) are obtained
using only 5 samples in the 33D parameter space. Hence, a total of 170 model runs are needed in this case
including for gradient computation using finite difference. Whereas, as discussed earlier,
constructing the sparse PCE itself requires model runs at 500 training points to sufficiently converge. Additional
model runs ($\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$) are required to further verify the accuracy of the 
resulting PCE. Note that the analysis was performed
for the fuel-rich case. However, similar trends are expected for the fuel-lean case and we do not include them here
for brevity.

In addition to the potential for computational cost reduction using the proposed framework, the comparative 
analysis also reveals the significant increase in computational effort associated with the PCE-based approach for
computing  the total-effect
Sobol' indices as the dimensionality increases from 19 to 33 despite using an efficient approach involving
sparse-basis PCEs. It can thus be understood that for higher dimensional problems involving hundreds of 
parameters, conventional approaches (even sparse-basis PCEs) can quickly become prohibitive and
the proposed DGSM-based approach could help
reduce the computational effort by several orders of magnitude.

### 2018-10-27 Paper/disc.tex
..

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its
potential for identifying the unimportant model inputs. \rebut{In fact, in 
the numerical tests and the chemical kinetics application presented in this
work, reasonable estimates of the screening metric are obtained during the
initial screening step with only 5 samples. This is indicative of a small
degree of
variability in the gradient of the model output with respect to individual
parameters, and therefore, a low variance of the Monte Carlo estimator.}
These observations could be exploited to construct efficient model surrogates
in a reduced input space. However, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, enhances the accuracy of the PCE-based surrogates as well.  
\rebut{Moreover, in the presence of severe non-linearities in the model output
leading to significant variability in its gradient in the considered input domain,
the number of samples and hence, the computational effort associated with
the estimation of screening metrics would expectedly 
increase. The extent of increase in the effort would of course depend upon the
application. In the case of rare events, the variance-based methods typically
lead to inaccurate estimates of the uncertainty in the model output. Since the
methodology proposed in this work is based on reducing computational
effort associated with variance-based sensitivity analysis, specifically, the
total-effect Sobol' index, it might lead to erroneous estimates of the
screening metrics and consequently the relative importance of the
uncertain parameters.}
Additionally, the proposed framework does not
account for the existence of possible correlations between the uncertain
inputs of the model. However, while the assumption of independent
inputs is not always justified, in many cases, correlations between
inputs are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs. On the other
hand, if approximate correlations are known, we recommend using a Gaussian 
process or Kriging-based surrogate since it 
provides a means for incorporating the correlation between inputs.  
Implementation to applications involving strongly correlated parameters
could enhance the applicability of the proposed framework. 
We consider that to be a potential direction for future studies related
to this work.

>>>>

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its
potential for identifying the unimportant model inputs. \rebut{In fact, in 
the numerical tests and the chemical kinetics application presented in this
work, reasonable estimates of the screening metric are obtained during the
initial screening step with only 5 samples. This is indicative of a small
degree of
variability in the gradient of the model output with respect to individual
parameters, and therefore, a low variance of the Monte Carlo estimator.}
These observations could be exploited to construct efficient model surrogates
in a reduced input space. However, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, enhances the accuracy of the PCE-based surrogates as well.  
\rebut{Moreover, in the presence of severe non-linearity in the model output
leading to significant variability in its gradient in the considered input domain,
the number of samples and hence, the computational effort associated with
the estimation of screening metrics would expectedly 
increase. The extent of increase in the effort would of course depend upon the
application. In the case of rare events, the variance-based methods typically
lead to inaccurate estimates of the uncertainty in the model output. Since the
methodology proposed in this work is based on reducing computational
effort associated with variance-based sensitivity analysis, specifically, the
total-effect Sobol' index, it might lead to erroneous estimates of the
screening metrics and consequently the relative importance of the
uncertain parameters.}
Additionally, the proposed framework does not
account for the existence of possible correlations between the uncertain
inputs of the model. However, while the assumption of independent
inputs is not always justified, in many cases, correlations between
inputs are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs. On the other
hand, if approximate correlations are known, we recommend using a Gaussian 
process or Kriging-based surrogate since it 
provides a means for incorporating the correlation between inputs.  
Implementation to applications involving strongly correlated parameters
could enhance the applicability of the proposed framework. 
We consider that to be a potential direction for future studies related
to this work.
